---
title: Epidemic dynamics of the sudden oak death pathogen Phytophthora ramorum in
  Oregon forests
author: "Carleson et al."
date: "December 17, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libs

```{r load_libs}
library(ggplot)
library(viridis)
library(scales)

library(magrittr)
library(dplyr)
library(forcats)

library(ape)
library(adegenet)
library(poppr)
```


## Figures

Prepare for analysis by establishing some basic parameters and loading files

```{r prep_analysis}
# load R data
# SSRs
load("data/genclones_from_SSRs.Rd")
# metadata
load("data/sample_info_all.Rd")


# Specify repeat lengths and then put in same order as appears in genind
repeat_lens <- c(2,2,	6,6,6,	2,	4,	2,	2,	2,	3,	4,	2,2,	4)
names(repeat_lens) <- c("ILVOPrMS79a",	"ILVOPrMS79b",
                        "PrMS145a", "PrMS145b", "PrMS145c",
                        "KIPrMS18",
                        "PrMS45",
                        "KIPrMS64",
                        "PrMS39",
                        "Pr9C3",
                        "PrMS6",
                        "ILVOPrMS131",
                        "KIPrMS82a",	"KIPrMS82b",
                        "PrMS43")

```

### Figure 3

Get pairwise distances and format into a tidy dataframe

```{r prep_dists}
# calc distances
setPop(ssrs_filtered) <- ~Lineage
ssrs_filtered_cc <- clonecorrect(ssrs_filtered, strata = ~Lineage)
all_dist <- bruvo.dist(ssrs_filtered_cc, replen = repeat_lens)

# format
dist_to_long <- function(dist) {
  if (class(dist) != "dist") stop("Must use dist object")
  A <- attr(dist, "Size")
  B <- if (is.null(attr(dist, "Labels"))) sequence(A) else attr(dist, "Labels")
  if (isTRUE(attr(dist, "Diag"))) attr(dist, "Diag") <- FALSE
  if (isTRUE(attr(dist, "Upper"))) attr(dist, "Upper") <- FALSE
  data.frame(
    row = B[unlist(lapply(sequence(A)[-1], function(x) x:A))],
    col = rep(B[-length(B)], (length(B)-1):1),
    value = as.vector(dist))
}

dist_df <- dist_to_long(all_dist)
```

```{r distance_hist_figs_paper}
ggplot(dist_df) +
  geom_histogram(aes(value, fill = Comparison, group = Comparison),
                 binwidth =0.02, color = "black", size = .3) +
  labs(x = "Pairwise genetic distance", y = "Count", fill = "") +
  scale_fill_manual(values =c("purple4", "orange2", "brown"),
                    breaks =c("EU1;EU1", "NA1;NA1", "EU1;NA1"),
                    labels = c("Within EU1", "Within NA1", "Among EU1 and NA1")) +
  scale_y_continuous(labels = comma, trans = "sqrt", breaks = c(100, 1000, 5000, 10000)) +
  theme_bw() +
  guides(fill = guide_legend(nrow = 1, keywidth = 0.3, keyheight = 0.3)) +
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        # legend.position = "bottom",
        legend.position = c(0.6, 0.9),
        legend.margin = margin(0,5,0,0),
        legend.box.margin = margin(0,0,0,0),
        axis.title.x =  element_text(size = 7),
        axis.title.y =  element_text(size = 7, margin = margin(0, 0, 0, 0)),
        axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 6, angle = 60),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        legend.box.spacing = margin(0,0,0,0),
        legend.spacing.x = unit(.1, "cm"))
ggsave("figs/pairwise_dists_v2.tiff", width = 3.25, height = 2, units = "in")

```

### Figure 4

```{r ranges_prep}
# pick the top N most abundant NA1 MLGs to visualize
top_n_mlgs <- production_samples %>%
  dplyr::group_by(MLG, Lineage) %>%
  dplyr::summarize(count = dplyr::n()) %>%
  arrange(desc(count)) %>%
  top_n(15, count)
top_n_mlgs <- rbind(
  production_samples %>%
    dplyr::filter(Lineage == "NA1") %>%
    dplyr::group_by(Lineage, MLG) %>%
    dplyr::summarize(count = dplyr::n()) %>%
    arrange(desc(count)) %>%
    top_n(15, count) %>%
    slice(1:15),
  production_samples %>%
    dplyr::filter(Lineage == "EU1") %>%
    dplyr::group_by(Lineage, MLG) %>%
    dplyr::summarize(count = dplyr::n()) %>%
    arrange(desc(count)) %>%
    top_n(15, count) %>%
    slice(1:15)
)
top_n_NA1_allEU1 <- rbind(
  production_samples %>%
    dplyr::filter(Lineage == "NA1") %>%
    dplyr::group_by(Lineage, MLG) %>%
    dplyr::summarize(count = dplyr::n()) %>%
    arrange(desc(count)) %>%
    top_n(15, count) %>%
    slice(1:15),
  production_samples %>%
    dplyr::filter(Lineage == "EU1") %>%
    dplyr::group_by(Lineage, MLG) %>%
    dplyr::summarize(count = dplyr::n()) %>%
    arrange(desc(count))
)

# get data and format correctly
ssrs_filtered_sub45 <- ssrs_filtered[ssrs_filtered@mlg[] %in% top_n_NA1_allEU1$MLG]
setPop(ssrs_filtered_sub45) <- ~Year/Lineage

rangers <- mlg.crosspop(ssrs_filtered_sub45, mlgsub = unique(ssrs_filtered_sub45@mlg), df = TRUE, quiet = TRUE) %>%
  arrange(desc(Count))
rangers$Lineage <- str_split(rangers$Population, "_", simplify = TRUE)[,2]
rangers$Year <- str_split(rangers$Population, "_", simplify = TRUE)[,1]
# names(rangers)[2] <- "Year"
rangers_mlg_order <- aggregate(rangers$Count, by = list(Category = rangers$MLG), FUN=sum) %>%
  arrange(desc(x)) %>%
  select(Category)
  
rangers$MLG <- factor(rangers$MLG, levels = rev(rangers_mlg_order$Category))
```

```{r ranges}
ranges <- ggplot(rangers, aes(x = Year, y = MLG, group = MLG)) + 
  geom_line(aes(color = Lineage), size = 1, linetype = 1) + 
  geom_point(aes(color = Lineage, shape = Lineage), fill = "white", size = 4.5) +
  scale_shape_manual(values = c(24, 21)) +
  scale_color_manual(values =c("orange2", "purple4")) +
  geom_text(aes(label = Count, fontface = 2), size = 3) + 
  labs(color = "Lineage:", shape = "Lineage:") +
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 6),
        axis.text.y = element_text(size = 6),
        # text = element_text(family = "serif"),
        legend.text = element_text(size = 6),
        legend.title = element_text(size = 7),
        legend.position = "bottom",
        axis.line = element_line(colour = "black"),
        axis.title = element_blank(),
        legend.box.margin = margin(0,0,0,0),
        legend.margin = margin(0,0,0,0))
ranges
ggsave("figs/mlg_by_year_v2.tiff", ranges, width = 3.25, height = 9.5, units = "in")

```

### Figure 5

#### A

PCA dataframe prep

```{r fig5_prep}
# Calculate PCA
scalegen.na1 <- scaleGen(ssrs_filtered_NA1, scale = FALSE, NA.method = "mean")
pca.na1 <- dudi.pca(scalegen.na1, center = FALSE, scale = FALSE,
                    scannf = FALSE, nf = 8)

# convert to dataframe object for ggplot
pca.na1.df <- data.frame(Isolate = rownames(pca.na1$li),
                         Lineage = factor(production_samples$Lineage[
                           production_samples$Lineage == "NA1"][
                             match(production_samples$Grunwald_isolate_ID[
                               production_samples$Lineage == "NA1"],
                               rownames(pca.na1$li))]),
                         Year = factor(production_samples$Year[
                           production_samples$Lineage == "NA1"][
                             match(production_samples$Grunwald_isolate_ID[
                               production_samples$Lineage == "NA1"],
                               rownames(pca.na1$li))]),
                         Watershed = factor(production_samples$Watershed_abbr[
                           production_samples$Lineage == "NA1"][
                             match(production_samples$Grunwald_isolate_ID[
                               production_samples$Lineage == "NA1"],
                               rownames(pca.na1$li))]),
                         Axis1 = pca.na1$li$Axis1,
                         Axis2 = pca.na1$li$Axis2,
                         Axis3 = pca.na1$li$Axis3)

# Fix watershed column and re-order
pca.na1.df$Watershed <- as.character(pca.na1.df$Watershed)
pca.na1.df$Watershed[pca.na1.df$Watershed %in% c("HuCr", "TuCr")] <- "Other"
watershed_order <- c("ChRv", "WiRv", "PiRv", "ThCr", "MyCr", "Other")
pca.na1.df$Watershed <- factor(pca.na1.df$Watershed, levels = watershed_order)

# Additional info for plotting
pca.na1.variance <- pca.na1$eig/sum(pca.na1$eig)
pca.na1.labels <- paste(colnames(pca.na1$li),
                        paste("(", as.character(round(pca.na1.variance[1:8]*100, 2)),
                              "%", ")",
                              sep = ""))

# K-means clustering in to k = n.clust groups
set.seed(102)
clusters_NA1 <- find.clusters(ssrs_filtered_NA1, n.pca=35, n.clust = 3)
grp_NA1 <- clusters_NA1$grp
pca.na1.df$Cluster <- grp_NA1
```

PCA: fill = watershed, shape = cluster

```{r fig5_pca}
pca.na1.df.no_other <- pca.na1.df %>% 
  filter(Watershed != "Other")
  
# Color-blind friendly palette from here, with a couple of colors shuffled
# http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/#a-colorblind-friendly-palette
cbPalette <- c("#999999", "#D55E00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#E69F00", "#CC79A7")

set.seed(102)
ggplot(pca.na1.df.no_other, aes(x = Axis1, y = Axis2)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  xlab(pca.na1.labels[1]) + ylab(pca.na1.labels[2]) +
  geom_jitter(aes(group = Cluster, fill = Watershed, shape = Cluster), size = 1.75, alpha = 0.5, height = 0.025, width = 0.025) +
  stat_ellipse(aes(Axis1, Axis2, group = Cluster, color = Cluster), size = 0.5, alpha = 0.9, inherit.aes = FALSE) +
  scale_color_viridis_d(option = "viridis") +
  # scale_fill_viridis_d(option = "inferno") +
  scale_fill_manual(values = cbPalette) +
  scale_shape_manual(values = c(22, 21, 25)) +
  theme_bw() +
  guides(color = guide_legend(override.aes =
                                list(size = 2, alpha = 0.5)),
                              # nrow = 1, keywidth = 0.3, keyheight = 0.3),
         fill = guide_legend(override.aes =
                               list(size = 2, shape = 21, alpha = 0.75),
                             nrow = 2, keywidth = 0.3, keyheight = 0.3)) +
  theme(panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.margin = margin(0,5,0,0),
        legend.box.margin = margin(0,0,0,0),
        axis.title =  element_text(size = 8),
        axis.text = element_text(size = 6),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.box.spacing = margin(0,0,0,0),
        legend.spacing.x = unit(.1, "cm"))
ggsave("figs/pca_na1_fillwatershed_shapecluster_ellipsecluster_v2_Ax1Ax2.tiff", width = 7, height = 3)


set.seed(102)
ggplot(pca.na1.df.no_other, aes(x = Axis1, y = Axis3)) +
  geom_hline(yintercept = 0) +
  geom_vline(xintercept = 0) +
  xlab(pca.na1.labels[1]) + ylab(pca.na1.labels[3]) +
  geom_jitter(aes(group = Cluster, fill = Watershed, shape = Cluster), size = 1.75, alpha = 0.5, height = 0.025, width = 0.025) +
  stat_ellipse(aes(Axis1, Axis3, group = Cluster, color = Cluster), size = 0.5, alpha = 0.9, inherit.aes = FALSE) +
  scale_color_viridis_d(option = "viridis") +
  # scale_fill_viridis_d(option = "inferno") +
  scale_fill_manual(values = cbPalette) +
  scale_shape_manual(values = c(22, 21, 25)) +
  theme_bw() +
  guides(color = guide_legend(override.aes =
                                list(size = 2, alpha = 0.5)),
                              # nrow = 1, keywidth = 0.3, keyheight = 0.3),
         fill = guide_legend(override.aes =
                               list(size = 2, shape = 21, alpha = 0.75),
                             nrow = 2, keywidth = 0.3, keyheight = 0.3)) +
  theme(panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.margin = margin(0,5,0,0),
        legend.box.margin = margin(0,0,0,0),
        axis.title =  element_text(size = 8),
        axis.text = element_text(size = 6),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.box.spacing = margin(0,0,0,0),
        legend.spacing.x = unit(.1, "cm"))
ggsave("figs/pca_na1_fillwatershed_shapecluster_ellipsecluster_v2_Ax1Ax3.tiff", width = 7, height = 3)
```

#### B

In 5a, find.cluster is an implementation of DAPC clustering.
It runs K-means clustering on the PCA transformation of our data.
The posterior probability of every isolate being assigned to each cluster are sorted and plotted by year (B) and by watershed (C)

```{r dapc_na1_clusters}
# calculate DAPC
pop(ssrs_filtered_NA1) <- grp_NA1
set.seed(102)
dapc_na1_kclust <- dapc(ssrs_filtered_NA1, grp = grp_NA1, n.pca = 50, n.da = 4)
optimization <- optim.a.score(dapc_na1_kclust)
dapc_na1_kclust <- dapc(ssrs_filtered_NA1, grp = grp_NA1, n.pca = optimization$best, n.da = 4)

# Gather DAPC results into a data frame
dapc.results <- as.data.frame(dapc_na1_kclust$posterior)
dapc.results$Cluster <- pop(ssrs_filtered_NA1)
dapc.results$Isolate <- rownames(dapc.results)
dapc.results$Watershed <- pca.na1.df$Watershed
dapc.results$Year <- pca.na1.df$Year
dapc.results.gather <- gather(dapc.results, DAPC_Cluster, Posterior, -c(Cluster, Isolate, Watershed, Year))

# Employ sorting method seen commoly in "Structure plots"
dapc_sorted_ws <- dapc.results.gather %>%
  group_by(Watershed, DAPC_Cluster) %>%
  summarise(avg = mean(Posterior)) %>%
  right_join(dapc.results.gather, by = c("Watershed", "DAPC_Cluster")) %>%
  arrange(Watershed, desc(avg), desc(Posterior)) %>%
  select(-avg) %>%
  ungroup
dapc_sorted_yr <- dapc.results.gather %>%
  group_by(Year, DAPC_Cluster) %>%
  summarise(avg = mean(Posterior)) %>%
  right_join(dapc.results.gather, by = c("Year", "DAPC_Cluster")) %>%
  arrange(Year, desc(avg), desc(Posterior)) %>%
  select(-avg) %>%
  ungroup

```

composition plot by year

```{r compo_yr}
p_yr <- ggplot(dapc_sorted_yr, aes(x=fct_inorder(Isolate), y=Posterior, fill=DAPC_Cluster))
p_yr <- p_yr + geom_bar(stat='identity', width = 1) 
p_yr <- p_yr + scale_fill_viridis_d()
p_yr <- p_yr + facet_grid(vars(Year), scales = "free_y", space = "free_y")
p_yr <- p_yr + scale_y_continuous(expand = c(0,0))
p_yr <- p_yr + theme_bw()
p_yr <- p_yr + guides(fill = guide_legend("Cluster",
                                          override.aes =
                                            list(alpha = 0.75,size = 2),
                             nrow = 1, keywidth = 0.3, keyheight = 0.3))
p_yr <- p_yr + theme(axis.text.y = element_blank(),
                     axis.text = element_text(size = 6),
                     axis.ticks.y = element_blank(),
                     panel.grid.minor = element_blank(),
                     panel.grid.major.y = element_blank(),
                     legend.text = element_text(size = 8),
                     legend.title = element_text(size = 8),
                     legend.position = "bottom",
                     legend.box.margin = margin(0,0,0,0),
                     legend.box.spacing = margin(0,0,0,0),
                     legend.margin = margin(0,0,0,0),
                     legend.spacing.x = unit(.1, "cm"),
                     axis.title = element_text(size = 8),
                     strip.text.y = element_text(size = 7, angle = 0),
                     strip.switch.pad.wrap = unit(1, "points"),
                     panel.spacing = unit(0, "points"),
                     strip.background = element_rect(fill = "white"))
p_yr <- p_yr + labs(x = "Isolate")
p_yr <- p_yr + ylab("Posterior membership probability")
p_yr <- p_yr + coord_flip()
p_yr
ggsave("figs/compo_k3_year_v2.tiff", width = 3.25, height = 4, units = "in")
```

#### C

compo plot by watershed

```{r compo_ws}
p_ws <- ggplot(dapc_sorted_ws, aes(x=fct_inorder(Isolate), y=Posterior, fill=DAPC_Cluster))
p_ws <- p_ws + geom_bar(stat='identity', width = 1) 
p_ws <- p_ws + scale_fill_viridis_d()
p_ws <- p_ws + facet_grid(vars(Watershed), scales = "free_y", space = "free_y")
p_ws <- p_ws + scale_y_continuous(expand = c(0,0))
p_ws <- p_ws + theme_bw()
p_ws <- p_ws + coord_flip()
p_ws <- p_ws + guides(fill = guide_legend("Cluster",
                                          override.aes =
                                            list(alpha = 0.75,size = 2),
                             nrow = 1, keywidth = 0.3, keyheight = 0.3))
p_ws <- p_ws + theme(axis.text.y = element_blank(),
                     axis.text = element_text(size = 6),
                     axis.ticks.y = element_blank(),
                     panel.grid.minor = element_blank(),
                     panel.grid.major.y = element_blank(),
                     legend.text = element_text(size = 8),
                     legend.title = element_text(size = 8),
                     legend.position = "bottom",
                     legend.box.margin = margin(0,0,0,0),
                     legend.box.spacing = margin(0,0,0,0),
                     legend.margin = margin(0,0,0,0),
                     legend.spacing.x = unit(.1, "cm"),
                     axis.title = element_text(size = 8),
                     strip.text.y = element_text(size = 7, angle = 0),
                     strip.switch.pad.wrap = unit(1, "points"),
                     panel.spacing = unit(0, "points"),
                     strip.background = element_rect(fill = "white"))
p_ws <- p_ws + labs(x = "Isolate")
p_ws <- p_ws + ylab("Posterior membership probability")
p_ws
ggsave("figs/compo_k3_watershed_v2.tiff", width = 3.25, height = 4, units = "in")
```


## Supplementary figures

### Genotype accumulation curves

Figures S1, S4, S5

```{r gac_EU1}
set.seed(503)
genotype_curve(ssrs_filtered_EU1)
ggplot2::last_plot() +
  labs(x = "Number of loci sampled", y = "Multilocus genotypes recovered")
  
ggsave("figs/GAC_EU1.tiff", width = 3.5, height = 3.5)
```

```{r gac_NA1}
set.seed(503)
genotype_curve(ssrs_filtered_NA1)
ggplot2::last_plot() +
  labs(x = "Number of loci sampled", y = "Multilocus genotypes recovered") +
  
ggsave("figs/GAC_NA1.tiff", width = 6, height = 3.5)
```

```{r gac_both}
set.seed(503)
genotype_curve(ssrs_filtered)
ggplot2::last_plot() +
  labs(x = "Number of loci sampled", y = "Multilocus genotypes recovered") +

ggsave("figs/GAC_both.tiff", width = 6.5, height = 3.5)
```

### Supplementary figure S2

### Supplementary figure S3

### Supplementary figure S6

### Supplementary figure S7

```{r raincloud_prep_code}
source("scripts/R_rainclouds.R")
library(cowplot)
dist_to_long <- function(dist) {
  if (class(dist) != "dist") stop("Must use dist object")
  A <- attr(dist, "Size")
  B <- if (is.null(attr(dist, "Labels"))) sequence(A) else attr(dist, "Labels")
  if (isTRUE(attr(dist, "Diag"))) attr(dist, "Diag") <- FALSE
  if (isTRUE(attr(dist, "Upper"))) attr(dist, "Upper") <- FALSE
  data.frame(
    row = B[unlist(lapply(sequence(A)[-1], function(x) x:A))],
    col = rep(B[-length(B)], (length(B)-1):1),
    value = as.vector(dist))
}
```

```{r prep_raincloudplots_dists}
# add clustering to SSRs
ssrs_filtered_NA1_cc_cluster3 <- ssrs_filtered_NA1
addStrata(ssrs_filtered_NA1_cc_cluster3, name = "Cluster_k3") <- grp_NA1
setPop(ssrs_filtered_NA1_cc_cluster3) <- ~Cluster_k3
# remove isolates with < 99% identity to any single group
min_post <- 0.99
dapc_na1_subset <- dapc_na1_kclust_df
dapc_na1_subset$index <- seq(1:nrow(dapc_na1_subset))
dapc_na1_subset <- dapc_na1_subset[
  dapc_na1_kclust_df$Posterior1 >= min_post |
    dapc_na1_kclust_df$Posterior2 >= min_post |
    dapc_na1_kclust_df$Posterior3 >= min_post,]
ssrs_filtered_NA1_cc_cluster3 <- ssrs_filtered_NA1_cc_cluster3[dapc_na1_subset$index]
ssrs_filtered_NA1_cc_cluster3 <- clonecorrect(ssrs_filtered_NA1_cc_cluster3, strata = ~Cluster_k3)
NA1_cc_cluster3_dist <- bruvo.dist(ssrs_filtered_NA1_cc_cluster3, replen = repeat_lens)

dist_df_NA1_cc_cluster3 <- dist_to_long(NA1_cc_cluster3_dist)

# 3. Make new column for Isolate A lineage
dist_df_NA1_cc_cluster3$Cluster_row <- grp_NA1[
  match(dist_df_NA1_cc_cluster3$row, names(grp_NA1))]

# 4. Make new column for Isolate B lineage
dist_df_NA1_cc_cluster3$Cluster_col <- grp_NA1[
  match(dist_df_NA1_cc_cluster3$col, names(grp_NA1))]

# 5. Make new column (paste(Lineage_A, Lineage_B, sep ="v"))
dist_df_NA1_cc_cluster3$Cluster_Comparison <- paste(dist_df_NA1_cc_cluster3$Cluster_row, dist_df_NA1_cc_cluster3$Cluster_col, sep = ";")
```


```{r raincloud_plot}
# make summary table with a summary statistic for each comparison
# that way I can avoid drawing a geom_vline individually for each median
# at the very least, my code will be more legible by calculating these all in one
# I will need to pass this dataframe to the geom separately each time
# plot
k_dist_calc_order_breaks <- c("1;1", "1;2", "1;3", "2;2", "2;3", "3;3")
k_dist_calc_order_labs <- c("Within 1", "Among 1 & 2", "Among 1 & 3", "Within 2", "Among 2 and 3", "Within 3")
ggplot(dist_df_NA1_cc_cluster3, aes(x = Cluster_Comparison, y = value,
                    colour = Cluster_Comparison, fill = Cluster_Comparison, group = Cluster_Comparison)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0),adjust =1.5) +
  geom_point(position = position_jitter(width = .15), size = .1, alpha = 0.2)+
  geom_boxplot(position = position_nudge(x=0.2), outlier.shape = NA, alpha = 0.3, width = .2, colour = "BLACK") +
  labs(y = 'Pairwise genetic distance', x = 'K-means clusters')+
  theme_cowplot()+
  scale_x_discrete(breaks = k_dist_calc_order_breaks,
                   labels = k_dist_calc_order_labs) +
  guides(fill=FALSE, colour = FALSE) +
  theme(axis.text.y = element_text(angle = 60)) +
  scale_colour_manual(values = cbPalette,
                    breaks = k_dist_calc_order_breaks,
                    labels = k_dist_calc_order_labs) +
  scale_fill_manual(values = cbPalette,
                    breaks = k_dist_calc_order_breaks,
                    labels = k_dist_calc_order_labs) +
  coord_flip()#+

ggsave("figs/NA1_cluster_genet_dists_v2.tiff", width = 7, height = 4, units = "in")

```

